
\begin{abstract}
\label{sec:abstract}

Cyber-Physical Systems (CPS) are increasingly utilizing advances in wireless mesh networking among computing nodes to facilitate communication and control for distributed applications.  Factors such as interference or node mobility cause such wireless networks to experience changes in both topology and link capacities.  These dynamic networks pose a reliability concern for high-criticality or mixed-criticality systems which require strict guarantees about system performance and robustness prior to deployment.  To address the design- and run-time verification and reliability concerns created by these dynamic networks, we are developing an integrated modeling, analysis, and run-time toolsuite which provides (1) network profiles that model the dynamics of system network resources and application network requirements over time, (2) design-time verification of application performance on dynamic networks, and (3) management of the CPS network resources during run-time.  In this paper we present the foundations for the analysis of dynamic networks and show experimental validations of this analysis.  We conclude with a focus on future work and applications to the field.

Cyber-Physical Systems (CPS) are becoming increasingly more distributed in nature, following the trend towards the internet of things (IoT) devices.  These distributed systems interact closely with the physical world and require the use of communications channels between the hardware nodes of the system as well as to external systems.  Since such systems are generally remotely deployed and managed, applications which are deployed onto the systems must be analyzed and verified in some way to ensure that the system can provide the application's required services and that the application will not degrade the overall system's functionality.  As these systems become more distributed in nature and rely more heavily on the network for communications, the network utilization and resources are becoming larger factors in the analysis and verification of distributed CPS and their applications.  In our work, we developed analysis techniques for very accurately and precisely predicting run-time application network performance and resource utilization from design-time models of the application network resource requirement profiles and system network resource provision profiles.  We showed how these models could be used to describe applications on wireless networks communicating using shared channel protocols, e.g. TDMA, as well as other medium access protocols, e.g. FDMA.  We experimentally validated these analysis techniques using run-time network emulation to enforce the system network resource profiles and application code which generated network traffic according to the applications' network resource requirement profiles.  Furthermore, we extended these analysis techniques to be implemented in a middleware stack that provided anonymous publish/subscribe and asynchronous/synchronous method invocation.  Our middleware extension measured the data production of each application and compared it against the application's network resource requirement profile.  By comparing the stated resource requirements to the application's actual resource utilization, we could detect deviations from the supplied profile and take action based on some condition.  For our implementation, we assumed any traffic which violated the supplied profile was anomalous and therefore we discarded it before it made it into kernel space.  Finally, we developed a component model for Robot Operating System (ROS) middleware, into which we are integrating our monitoring and analysis techniques.  We plan on using this infrastructure and our distributed Resilient CPS testbed to perform application and system network modeling and analysis tests, such as network anomaly classification.  We hope our modeling and analysis techniques and tools will be useful for designing, verifying, and deploying resilient distributed CPS.


%As Cyber-Physical Systems (CPS) become more common, both the systems and their applications grow in complexity.  Such complexity requires more run-time management of these applications, as well as new design-time analysis for verification that these applications will execute their mission without performance degradation. New tools are required for the design, analysis, and deployment of these complex, managed CPS applications.  To address this requirement, this paper presents a work-in-progress of a new toolsuite and infrastructure which provides capabilities for application and system design, design-time constraint checking, and run-time deployment and management of CPS applications. The focus of this paper is on the design, analysis, and run-time management of the communications network of the CPS applications.  We present the first results towards variable network analysis integrated into both the design time toolsuite and the run-time management software.
\end{abstract}


